Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-11-02 Arxiv/main.tex
Update Arxiv/main.tex
fix sensitivity proof
Update Arxiv/main.tex
fix typos

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Princeton University. {mbun@cs.princeton.edu}}
\date{}
\maketitle
{\small \tableofcontents}

@@

By Equation (\ref{eq_smooth}):
\begin{equation*}
\begin{split}
S(\dataobs) 
& \geq \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')}\\
\frac{1}{S(\dataobs)} 
& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')\\
\end{split}
\end{equation*}

@@

\begin{equation*}
\begin{split}
& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs''))\\
& = \gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\\
& = \gamma + \frac{1}{S(\dataobs')}
\end{split}
\end{equation*}
$\implies$
\begin{equation*}
\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
\end{equation*}

@@

\subsubsection{$\hexpmech$ Proposition}

@@

This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and by replacing the $\candidateset$ with set of posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
will denote by $\hexpmechd$ the mechanism for the
Dirichlet-multinomial system.

@@

\subsection{Privacy Analysis for Baseline Mechanisms}
In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \cite{dwork2014algorithmic}. The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \cite{dwork2014algorithmic}.

\subsubsection{$\hexpmech$ $\epsilon-$Differential Privacy Proof}

>>>>

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Princeton University. {mbun@cs.princeton.edu}}
\date{}
\maketitle
{\footnotesize \tableofcontents}

@@

By Equation (\ref{eq_smooth}):
\begin{equation*}
\begin{split}
S(\dataobs) 
& = \max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \}\\
\frac{1}{S(\dataobs)} 
& = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'') \bigg \}\\
\end{split}
\end{equation*}

@@

\begin{equation*}
\begin{split}
& \leq \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{  \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs'')) \bigg \}\\
& = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
\gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg 
\}\\
& = \gamma + \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg 
\}\\
& = \gamma + \frac{1}{S(\dataobs')}
\end{split}
\end{equation*}
$\implies$
\begin{equation*}
\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
\end{equation*}

@@

\subsection{$\hexpmech$ Proposition}

@@

This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and by replacing the $\candidateset$ with set of posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
will denote by $\hexpmechd$ the mechanism for the
Dirichlet-multinomial system.

@@

% \subsection{Privacy Analysis for Baseline Mechanisms}
% In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \cite{dwork2014algorithmic}. The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \cite{dwork2014algorithmic}.

\subsection{$\hexpmech$ $\epsilon-$Differential Privacy Proof}
